Response to the defense feedback

### 2021-05-31 Chapter-5/Chapter-5.tex
Updates from Overleaf

\subsection{Step 1: Fuzzing}
After we build the software into the binary executable, we give the binary code the random inputs. For cryptography libraries, the input is the encryption key. For non-cryptography libraries, the input could be images, text, and information in other formats. Encryption algorithms like AES, DES take an array representing the secrets. We generate the random input by flipping each bit of the keys. Some other programs also take a buffer as the input. The buffer may contain the redundancy information and follow a specific format. So not any input that satisfies the input length is a valid input. Under the circumstance, we have a dictionary that contains the input. For example, Crypto libraries usually take PKCS \#1 as the input of RSA private key. We use some other tools to generate a list of valid keys and use the key to sample the program. Due to the enormous search space, we can not iterate every input. However, our method can give a conservative estimate of each leakage site.
\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input secret. We use the dynamic binary instrumentation (DBI) tool to record whether a particular memory access information is accessed or not. Inspired by the AFL and Valgrind, we use the bitmap to represent whether a particular memory is accessed or not. For example, the bitmap ${0101}$ of address $address_1, address_2, address_3, address_4$ means that $address_2, address_4$ are hit during the execution. During the execution, the direct information we get is the virtual memory address (VMA). However, we transfer the address into the offset (Load Memory Address (LMA)) in the original binary file. It has two benefits. First, modern computer systems employ the Address Space Layout Randomization (ASLR). With ASLR, the operating system randomly puts the enclave code and data at various memory offset. As a result, the code will get different execution traces even for the same input because the enclave image is loaded at a different address each time. Second, it helps us find the leakage site in the source code.

We rely on the program header and symbol information to recover the offset in the binary. During the loading process, the operating system maps each segment into a contiguous memory region. So the offset of the virtual memory address between the code within the same segment is the same as the offset within the binary file. We choose the start address of some common functions (e.g, $main$) ($b$) as the navigation function. We get the virtual memory address of the start of the function ($\mathit{VMA_b}$) from the DBI tool and the load memory address of the function ($\mathit{LMA_b}$) from the symbol information. For any virtual address, we use Equation~\ref{equ:eq6} to calculate the offset in the original address.
\begin{equation}\label{equ:eq6}
  \mathit{LMA_a} = \mathit{LMA_b} - VMA_b - VMA_a
\end{equation}

There are two kinds of memory accesses: accesses to the code and accesses to the data.
\begin{itemize}
  \item Code Access. The memory address of the code is the value of $rip$ register. However, the length of x86 instructions can be from 1 byte to 15 bytes. For instructions whose length is longer than one byte, we also update the address after the value $rip$ until the address reaches the instruction's boundary.
  \item Data Access. For instructions with memory access, we identify all the operands of each instruction and. Same as the code address, the instruction can read or write multiple bytes one time.  Instructions like \textsf{push} and \textsf{pop} have implicit memory access. We all update the bitmap of the address correspondingly.
\end{itemize}

@@

\subsubsection{Various Granularities Side-channel Detection}
\ctool{} can detect the side-channel vulnerabilities in different granularities. For each granularity, we calculate a new bitmap that represents access information of each unit. We have the bitmap of the memory access at the byte level. An attacker who has the coarse-grained observation at address space may not distinguish the address difference. For example, modern X64 computer systems use 48-bit virtual memory addresses. The top 36 bit of the virtual address is called Virtual Page Number (VPN), and the bottom 12 bits of the virtual address is called offset. The memory management unit (MMU) transfers the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keeping the offset of the address. So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the page-level observation.

Suppose a program reads one byte at memory $\mathsf{0x7ffff7ffd001}$ when the secret is $k_1$ and reads a different byte at memory $\mathsf{0x7ffff7ffda01}$ when the secret is $k_2$, an attacker who has the page-level observation can not launch the attack but an attacker who launches the cache attack can know the input is $k_1$ or $k_2$. We update the new bitmap of the large unit by merging the bitmaps of small units that fall into the large unit. That is, $\forall addr_1, addr_2, \dots, addr_n \in addr_N, B^{addr_N}_{k_i} = B^{addr_1}_{k_i} \lor,\dots,\lor B^{addr_N}_{k_n}$.

\subsubsection{Leakage Detection} The access of the address is secret-dependent if $ \exists\, k_{i1}, k_{i2} \in K, \, B^{addr}_{k_i1} \oplus  B^{addr}_{k_i2} =1 $. In the chapter, we perform the logical exclusive OR operation on every boolearn value in the same address. If the result is $1$, then the address is vulnerable to the side-channel attacks.

\begin{myexample}
Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathsf{7ffff7ffd000}$ to $\mathsf{7ffff7ffd03f}$ (One cache line). We perform the bit-wise or operation of each address with the address range. Because the cache line is always accessed. We think it is not a leak here.
\begin{center}
  \begin{tabular}{c}
    {
      \begin{lstlisting}[frame=none]
              k1  k2  k3  k4  k5  k6  k7  k8   Result  
7ffff7ffd000   1   0   1   0   1   1   0   1 
7ffff7ffd000   0   1   1   0   1   1   1   1 
7ffff7ffd000   1   1   1   1   1   1   0   1 
7ffff7ffd000   1   0   1   0   1   1   1   1 
...
7ffff7ffd03f   1   0   1   0   1   1   1   0  
cache line     1   1   1   1   1   1   1   1    0 (No Leaks)
\end{lstlisting}
    }
  \end{tabular}
\end{center}
\end{myexample}

>>>>

\subsection{Step 1: Fuzzing}
After we build the software into the binary executable, we give the
binary code the random inputs. For cryptography libraries, the input
is the encryption key. For non-cryptography libraries, the input could
be images, text, and information in another format. Encryption
algorithms like AES and DES take an array representing the secrets. We
generate the random input by flipping each bit of the keys. Some other
programs also take a buffer as the input. The buffer may contain the
redundancy information and follow a specific format. So not any input
that satisfies the input length is a valid input. Under the
circumstance, we have a dictionary that contains the input. For
example, crypto libraries usually take PKCS \#1 as the input of the
RSA private key. We use some other tools to generate a list of valid
keys and use the key to sample the program. Due to the enormous search
space, we can not iterate every input. However, our method can give a
conservative estimate of each leakage site.
\subsection{Step 2: Address Record}
Next, we record the memory access information based on the input
secret. We use the dynamic binary instrumentation (DBI) tool to record
whether a particular memory access information is accessed or
not. Inspired by the AFL and Valgrind, we use the bitmap to represent
whether a particular memory is accessed or not. For example, the
bitmap ${0101}$ of address $l_1, l_2, l_3, l_4$ means that $l_2, l_4$
are hit during the execution. During the execution, the direct
information we get is the virtual memory address (VMA). However, we
transfer the address into the offset (Load Memory Address (LMA)) in
the original binary file. It has two benefits. First, modern computer
systems employ the Address Space Layout Randomization (ASLR). With
ASLR, the operating system randomly puts the enclave code and data at
various memory offset. As a result, the code will get different
execution traces even for the same input because the enclave image is
loaded at a different address each time. Second, it helps us find the
leakage site in the source code.

We rely on the program header and symbol information to recover the
offset in the binary. During the loading process, the operating system
maps each segment into a contiguous memory region. So the offset of
the virtual memory address between the code within the same segment is
the same as the offset within the binary file. We choose the start
address of some common functions (e.g, $\mathit{main}$) ($b$) as the navigation
function. We get the virtual memory address of the start of the
function ($\mathit{VMA}_b$) from the DBI tool and the load memory
address of the function ($\mathit{LMA}_b$) from the symbol
information. For any virtual address, we use Equation~\ref{equ:eq6} to
calculate the offset in the original address.
\begin{equation}\label{equ:eq6}
    \mathit{LMA}_a = \mathit{LMA}_b - \mathit{VMA}_b - \mathit{VMA}_a
\end{equation}

There are two kinds of memory access: access to the code and access to the data. 
\begin{itemize}
\item Code Access. The memory address of the code is the value of $\mathit{rip}$ register. However, the length of x86 instructions can be from 1 byte to 15 bytes. For instructions whose length is longer than one byte, we also update the address after the value $\mathit{rip}$ until the address reaches the instruction's boundary.
\item Data Access. For instructions with memory access, we identify all the operands of each instruction and. Same as the code address, the instruction can read or write multiple bytes one time.  Instructions like \textsf{push} and \textsf{pop} have implicit memory access. We all update the bitmap of the address correspondingly.
\end{itemize}

@@

\subsubsection{Various Granularities Side-channel Detection}
\ctool{} can detect the side-channel vulnerabilities in different granularities. For each granularity, we calculate a new bitmap that represents access information of each unit. We have the bitmap of the memory access at the byte level. An attacker who has the coarse-grained observation at address space may not be able to distinguish the address difference. For example, modern X64 computer systems use 48-bit virtual memory addresses. The top 36 bit of the virtual address is called Virtual Page Number (VPN), and the bottom 12 bits of the virtual address is called offset. The memory management unit (MMU) transfers the virtual address into the physical address by mapping the Virtual Page Number (VPN) into the Physical Page Number (PPN) while keeping the offset of the address. So two addresses with the Same VPN but different offset are not distinguishable by an attacker who only has the page-level observation.

Suppose a program reads one byte at memory address
$\mathtt{0x7ffff7ffd001}$ when the secret is $k_1$ and reads a
different byte at memory $\mathtt{0x7ffff7ffda01}$ when the secret is
$k_2$, an attacker who has the page-level observation can not launch
the attack but an attacker who launches the cache attack can know the
input is $k_1$ or $k_2$. We update the new bitmap of the large unit by
merging the bitmaps of small units that fall into the large unit. That
is, $\forall
  l_1, l_2, \dots, l_n \in l_N, B^{l_N}_{k_i} = B^{l_1}_{k_i} \lor,\dots,\lor B^{l_n}_{k_n}$.

\subsubsection{Leakage Detection} 
The access of the address is secret-dependent if $ \exists\, k_{i_1}, k_{i_2} \in K, \, B^{l}_{k_{i_1}} \oplus  B^{l}_{k_{i_2}} =1 $. In the step, we perform the logical exclusive OR operation on every boolearn value in the same address. If the result is $1$, then the address is vulnerable to the side-channel attacks.

\begin{myexample}
Suppose we sample a program from $k1$ to $k8$ and record the memory access at the granularity of each byte from $\mathtt{7ffff7ffd000}$ to $\mathtt{7ffff7ffd03f}$ (One cache line). We perform the bit-wise or operation of each address with the address range. Because the cache line is always accessed. We think it is not a leak here.
\begin{center}
  \begin{tabular}{c}
    {
      \begin{lstlisting}[frame=none]
              k1  k2  k3  k4  k5  k6  k7  k8   Result  
7ffff7ffd000   1   0   1   0   1   1   0   1 
7ffff7ffd000   0   1   1   0   1   1   1   1 
7ffff7ffd000   1   1   1   1   1   1   0   1 
7ffff7ffd000   1   0   1   0   1   1   1   1 
...
7ffff7ffd03f   1   0   1   0   1   1   1   0  
cache line     1   1   1   1   1   1   1   1    0 (No Leaks)
\end{lstlisting}
    }
  \end{tabular}
\end{center}
\end{myexample}
